\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-06-29 write_up/mixfishsim_ecolmod.tex
Clean up text

\replaced[id = PD]{If fisheries are to avoid unwanted catch}{To implement
	effective spatial measures to reduce discards} a good understanding of
spatiotemporal fishery dynamics is required. However, traditional scientific
advice is limited by a lack of highly resolved knowledge of population
distributions, population movement and how fishers interact with different fish
populations. This reflects the fact that data on fish location at high temporal
and spatial resolutions is expensive and difficult to collect. Proxies inferred
from either scientific surveys or commercial catch data are often used to model
distributions, often with sparse data at limited spatial and temporal
resolution. \\

To understand how data resolution impacts inference on mixed fisheries
interactions, we develop a highly resolved spatiotemporal simulation model
incorporating: i) delay-difference population dynamics, ii) population movement
using Gaussian Random Fields to simulate patchy, heterogeneously distributed
populations, and iii) fishery dynamics for multiple fleet characteristics based
on species targeting via a mix of correlated random walk movement (for
exploration) and learned behaviour (for exploitation) phases of the fisheries.
\\

We simulate 50 years of fishing and use the results from the fisheries catch to
draw inference on the underlying population structures. We compare this
inference to a simulated fixed-site sampling design commonly used for fisheries
monitoring purposes and the true underlying population structures input to the
simulation. We i) use the results to establish the potential and limitations of
fishery-dependent data in providing a robust picture of spatiotemporal
distributions; and ii) simulate an area closure based on areas defined from the
different data sources at a range of temporal and spatial resolutions and
assess their effectiveness on reducing catches of a fish population. \\

@@

\replaced[id=PD]{Identifying}{Ensuring measures are implemented at} an
appropriate scale has been a challenge in the past that has led to ineffectual
measures with unintended consequences such as limited impact towards the
management objective or increased benthic impact on previously unexploited
areas (e.g. the cod closure in the North Sea
\citep{Rijnsdorp2001,Dinmore2003}). \replaced[id=PD]{M}{Since then m}ore
refined spatial information has \added[id=PD]{since} become available through
the combination of logbook and Vessel Monitoring System (VMS) data
\citep{Lee2010, Bastardie2010, Gerritsen2012, Mateo2016} and more real-time
spatial management has been possible \citep[e.g.][]{Holmes2011}.  Such
information is, however, derived from an inherently biased sampling programme,
targeted fishing, where fishers establish favoured fishing grounds first
through an explore-exploit strategy \cite{Bailey2018} and then use experience
to return to areas of high catch. \deleted[id=PD]{ Further, fishers generally
	only recorded landings (not catch) on a daily
	basis\todo{\added[id=JJ]{Its not clear what the problem is: landings
			collected on daily basis or landings recorded rather
			than catch}}.  This leads to questions about the
	validity of inference that can be drawn from landings data assigned to
	VMS activity pings.}\todo{\added[id=JJ]{This comes as a surprise: I
		thought this was going to be about
		discards}\added[id=PD]{Agree, have removed this to avoid
		confusion}}\\

@@

To answer these questions we i) develop a simulation model where population
dynamics are highly-resolved in space and time \replaced[id=PD]{. Being}{ and
	are} known \added[id=PD]{directly} rather than inferred from sampling
or commercial catch\added[id=PD]{, we can use the population model to evaluate
	how inference from fisheries-dependent and fisheries independent
	sampling relates to the real population structure}. We ii) compare, at
different spatial and temporal aggregations, the simulated population
distributions to samples from fisheries-dependent and fisheries independent
catches to test if these are a true reflection of the relative density of the
populations. We then iii) simulate a fishery closure to protect a species based
on different spatial and temporal data aggregations. We use these evaluations
to draw inference on the utility of commercial data in supporting management
decisions. \todo{\added[id=JJ]{If the paper has two goals this should be clear
		from the start, but may be better over 2 MSs}\added[id=PD]{I
		would like to keep both parts, but have made clearer in how its
		set out.  The closure scenarios form validation of the data
		aggregation, rather than effectiveness of the closures
		themselves - so its a continuation of the same question in my
		eyes}}\deleted[id=PD]{.  Further, we extend our analysis to a
	range of spatial and temporal scales to assess the impact of these
	processes on the success of the management measure.}\\

@@

The basic population level processes are simulated using a modified two-stage
Deriso-Schnute delay difference model \citep{Deriso1980, Schnute1985,
	Dichmont2003} occurring at a daily time-step. \added[id=PD]{A daily
	time-step was chosen to discretise continuous population processes
	on a biologically relevant and computationally tractable timescale.}
\replaced[id=PD]{Under the population dynamics module}{Here,} population
biomass growth and depletion for pre-recruits and\deleted[id=PD]{fish}
recruited \added[id=PD]{fish} \deleted[id=PD]{to the fishery} are modelled
separately as a function of previous recruited biomass, intrinsic population
growth and recruitment. Biomass for each cell $c$ is incremented each day $d$ as
follows (the full parameter list is detailed in Table \ref{tab: pop_variable}):
\begin{equation}
	\begin{split}
	B_{c,d+1} = &\\
	& (1 + \rho) B_{c,d} \cdot e^{-Z_{c,d}} - \rho \cdot e^{-Z_{c,d}} \hspace{2.9cm}
	\times \\  
	& (B_{c,d-1} \cdot e^{-Z_{c,d-1}} + Wt_{R-1} \cdot \alpha_{d-1} \cdot
	R_{\tilde{y}(c,y,d-1)})
	\hspace{0.4cm} + \\
	& Wt_{R} \cdot \alpha_{d} \cdot R_{\tilde{y}(c,y,d)} 
	\end{split}
\end{equation}
where $\rho$ is Brody's coefficient, shown to be equal to $e^{-K}$ when $K$ is
the growth rate from a von Bertalanffy logistic growth model
\citep{Schnute1985}. $Wt_{R-1}$ is the average weight of fish prior to
recruitment, while $Wt_{R}$ is the average recruited weight. $\alpha_{d}$
represents the proportion of fish recruited during that day for the year, while
$R_{c,\tilde{y}}$ is the annual recruits in cell $c$ for year $y$. \\

@@

Recruitment is modelled through a function relating the mature biomass to
recruits at time of recruitment. In \emph{MixFishSim}, it can be modelled
either either as a stochastic Beverton-Holt stock-recruit form
\citep{Beverton1957}: 
\begin{equation}
	\begin{split}
	\bar{R}_{c,d} = & \frac{(\alpha * S_{c,d})}{(\beta + S_{c,d})} \\
	     R_{c,d} \sim & \log N[(\log(\bar{R}_{c,d}),\sigma^2)]
	\end{split}
\end{equation}
Where $\alpha$ is the maximum recruitment rate, $\beta$ the spawning stock
biomass (SSB) required to produce half the maximum stock size, $S$ current
stock size and $\sigma^2$ the variability in the recruitment due to stochastic
processes, or a stochastic Ricker form \citep{Ricker1954}:
\begin{equation}
	\begin{split}
	\bar{R}_{c,d} = & B_{c,d} * e^{(\alpha - \beta * B_{c,d})} \\	
   	     R_{c,d} \sim & \log N[(\log(\bar{R}_{c,d}),\log(\sigma^2))]
	\end{split}
\end{equation}
where $\alpha$ is the maximum productivity per spawner and $\beta$ the density
dependent reduction in productivity as the SSB increases. In our example
application the Beverton-Holt form of stock recruit relationship was used for
all populations though either functional form can be chosen.

@@

During pre-defined weeks of the year the habitat quality is modified with
\added[id=PD]{user-defined} spawning habitat locations\deleted[id=PD]{s},
\replaced[id=PD]{resulting in}{meaning} each population
\replaced[id=PD]{having}{has} concentrated areas where spawning takes place. In
the simulations the populations move\replaced[id=PD]{d}{s} towards
\replaced[id=PD]{these cells}{this} in the weeks prior to spawning, resulting
in directional movement towards the spawning grounds.\todo{\added[id=JM]{What
		does it mean concisely? Areas are assigned?} \added[id=PD]{Yes,
		the areas are pre-defined - I have amended to reflect and tried
		to clarify}} \\

\replaced[id=JJ]{An}{, with an} advection-diffusion process \deleted[id=JJ]{to}
control\added[id=JJ]{led} \deleted[id=JJ]{how the} population\deleted[id=JJ]{s}
move\replaced[id=JJ]{ment}{d}, with a time-varying temperature covariate used
to change the interaction between time and suitable habitat on a weekly
time-step\todo{\added[id=JJ]{What have a temperature covariate? Could just use
		time}\added[id=PD]{Was intended as some biological meaning -
		species thermal tolerances load onto the temperature effect -
		so could be different per species}}.  \deleted[id=JJ]{This was
	intended to balance realism in population movement, capturing the main
	directed and random processes, and practicality of modelling the
	population rather than individual fish.} Each population $p$
\replaced[id=PD]{wa}{i}s assigned a thermal tolerance with mean,
$\mu\added[id=PD]{_{p}}$ and variance, $\sigma^2\added[id=PD]{_{p}}$ so that
each cell and population temperature suitability is defined that:
\begin{equation}
	Tol_{c, p\added[id=PD]{, wk}} = \frac{1}{ \sqrt (2\pi \cdot \sigma^2_{p})} \cdot \exp(-
		\frac{(T_{c\added[id=PD]{, wk}} - \mu_{p})^2}{2 \cdot \sigma^2_{p}} )	
\end{equation}
Where $Tol_{c, p, \added[id=PD]{wk}}$ is the tolerance of population $p$ for
cell $c$ \added[id=PD]{in week $wk$}, $T_{c, \added[id=PD]{wk}}$ is the
temperature in the cell \added[id=PD]{given the week} and
$\mu\added[id=PD]{_{p}}$ and $\sigma^2\added[id=PD]{_{p}}$ the mean and
standard deviation of the population temperature tolerance. \\

\added[id=PD]{The final process resulted in population structures and movement
	patterns unique to each species, with population movement occurring on
	a weekly basis. The decision to model population movement on a weekly
	timescale was to reflect that fish tend to aggregate in species
	specific locations and range within a week is fairly limited [REF!!].
	Therefore this process approximated the demographic shifts in fish
	populations throughout a year with seasonal spawning patterns (e.g.
	Figure \ref{S-fig:5}).}

@@

The fleet dynamics can be broadly categorised into three components; fleet
targeting - which determine\replaced[id=PD]{d}{s} the fleet catch efficiency
and preference towards a particular species; trip-level decisions, which
determine\added[id=PD]{d} the initial location to be fished at the beginning of
a trip; and within-trip decisions, determining movement from one fishing spot
to another within a trip. Together, these element implement an explore-exploit
type strategy for individual vessels to maximise their catch from an unknown
resource distribution (\cite{Bailey2018}). The decision to use an individual
based model for fishing vessels was taken because fishers as a group tend to
show heterogeneity and individual rather than group dynamics. Thus this was the
fleet dynamics is the productive of individual experiences rather than
pre-ordained group dynamics.

@@

Several studies \citep[e.g.][]{Hutton2004, Tidd2012, Girardin2015} have
confirmed past activity and past catch rates are strong predictors of fishing
location choice. For this reason, the fleet dynamics sub-model
include\replaced[id=PD]{d}{s} a learning component, where a vessel's initial
fishing location in a trip \replaced[id=PD]{wa}{i}s based on selecting from
previously successful fishing locations. This \replaced[id=PD]{wa}{i}s achieved
by \added[id=PD]{calculating an expected revenue based on the catches from
	locations fished} in the preceding trip as well as the same month
periods in previous years and the travel costs from the port to the fishing
grounds, and choosing randomly from the top 75 \% of fishing events
\replaced[id=PD]{as defined by the expected profit}{in value}.

@@

Where several fishing vessels exploit the same fish population competition is
known to play an important role in local distribution of fishing effort
\citep{Gillis1998}. If several vessels are fishing on the same patch of fish,
local depletion and interference \added[id=JJ]{competition} will affect fishing
location choice of the fleet as a whole \citep{Rijnsdorp2000, Poos2007a}. In
order to account for this behaviour, the fishing sub-model operates spatially
on a daily time-step so that for future days the biomass available to the
fishery is reduced in the areas fished. The cumulative effect is to make
heavily fished areas less attractive as future fishing opportunities.

@@

We parametrised the simulation model for four populations with different
demographics; growth rates, natural mortality and recruitment functions (Table
\ref{tab:1}). Habitat preference (Figure \ref{S-fig:1}) and temperature
tolerances (Figures \ref{S-fig:3}, \ref{S-fig:4}) were unique to each
population resulting in differently weekly distribution patterns (Figures
\ref{S-fig:5}-\ref{S-fig:7}). In addition, each of the populations has two
defined spawning areas which result in the populations moving towards these
areas in pre-defined weeks (Figure \ref{S-fig:2}) with population-specific
movement rates (Table \ref{tab:1}). The individual habitat preferences and
thermal tolerances results different spatial habitat use for each population
(Figure \ref{S-fig:9}) and consequently different seasonal exploitation
patterns (Fishing mortality in Figure \ref{S-fig:10}).

@@

The survey simulation was set up with follow a fixed gridded station design
with 100 stations fished each year, starting on day 92 \added[id=PD]{and ending
	on day 112 (5 stations per day)} with same catchability parameters for
all populations ($Q_{p} = 1$).

@@

The following steps are undertaken to determine closures:
\todo{\added[id=JJ]{Procedure unclear. Refer to symbols in methods section or
		switch order starting with description of data type
		etc..}\added[id=PD]{Yes, will redo}}
\begin{enumerate}
	\item Extract data source
	\item Aggregate according to desired spatial and temporal resolution
	\item Interpolate across entire area at desired resolution
	\item Close area covering top 5 \% of catch 
\end{enumerate}
In total 28 closure scenarios were run which represent combinations of:

@@

The trend in fishing mortality for each species show that in most cases the
fishery closure was successful in reducing fishing mortality on the species of
interest (species 3; Figure \ref{fig:3}), though interestingly the largest
reductions in fishing mortality happened immediately after the closures,
following which the fisheries "adapted" to the closures and fishing mortality
increased again somewhat. The exception to the success was the closures
implemented based on the coarsest spatial (20 x 20) and temporal resolution
which were ineffective with all data sources. As expected, closures based on
the "known" population distribution were most effective, with differing degrees
of success using the commercial data. Fishing mortality rates on the other
species changed in different proportions, depending on whether the displaced
fishing effort moved to areas where the populations were in more greater or
lesser density. \\

A regression tree highlights that the most factor contributing to differences
in fishing mortality before and after the closure was the population (72 \%
showing that the closures were effective for population 3), followed by data
resolution (21 \%), data type (7 \%) with the least important factor the
timescale ($<$ 1 \%). In general the finer the spatial resolution of the data
used the greater reduction in fishing mortality for population 3 after the
closures (Figure\ref{fig:4}). The notable outliers are the commercial data at
the coarsest spatial resolution (20 x 20) at a yearly and weekly timescale,
where closures were nearly as effective as the fine-scale resolution. In this
case the closures were sufficiently large to protect the population (and was as
effective as when the closure was based on the "real population") but this may
have consequences in terms of restricting a much larger area than necessary. \\

@@

Our study evaluates the importance of data scaling and considers potential bias
introduced through data aggregation when using commercial fisheries data to
infer spatio-temporal dynamics in fisheries. Understanding how fishers exploit
multiple heterogeneously distributed fish populations with different catch
limits or conservation status requires detailed understanding of the overlap of
resources; this is difficult to achieve using conventional modelling approaches
due to species targeting in fisheries resulting in preferential sampling
\cite{Martinez-Minaya2018}. Often data is aggregated or extrapolated which
requires assumptions about the spatial and temporal scale of processes. Our
study explores the assumptions behind such aggregation and preferential
sampling to identify potential impacts on management advice. With modern
management approaches increasingly employing more nuanced spatio-temporal
approaches in order to maximise productivity while taking account of both the
biological and human processes operating on different time-frames
(\cite{Dunn2016}), understanding assumptions behind the data used -
increasingly a combination of logbook and positional information from vessel
monitoring systems - is vital to ensure measures are effective. \\

We employ a simulation approach to model each of the population and fishery
processes in a hypothetical 'mixed fishery', allowing us to i) evaluate the
consequences of different aggregation assumptions on our understanding of the
spatio-temporal distribution of the underlying fish populations, and ii)
evaluate the effectiveness of a spatial closure given those assumptions. Our
approach captures fine scale population and fishery dynamics not usually
considered (although see \cite{Bastardie2010, Bailey2018}) which offers the
advantage that larger scale fishery patterns are emergent properties of the
system rather than the result of a statistical modelling framework. \\

>>>>

\replaced[id = PD]{If fisheries are to avoid unwanted catch}{To implement
	effective spatial measures to reduce discards} a good understanding of
spatiotemporal fishery dynamics is required. However, traditional scientific
advice is limited by a lack of highly resolved knowledge of population
distributions, population movement and how fishers interact with different fish
populations. This reflects the fact that data on fish location at high temporal
and spatial resolutions is expensive and difficult to collect. Proxies inferred
from either scientific surveys or commercial catch data are often used to model
distributions, usually with sparse data at limited spatial and temporal
resolution. \\

To understand how data resolution impacts inference on mixed fisheries
interactions, we develop a highly resolved spatiotemporal simulation model
incorporating: i) delay-difference population dynamics, ii) population movement
using Gaussian Random Fields to simulate patchy, heterogeneously distributed
populations, and iii) fishery dynamics for multiple fleet characteristics based
on species targeting under an explore-exploit strategy via a mix of correlated
random walk movement (for exploration) and learned behaviour (for exploitation)
phases of the fisheries.  \\

We simulate 50 years of fishing and use the results from the fisheries catch to
draw inference on the underlying population structures. We compare this
inference to a simulated fixed-site sampling design commonly used for fisheries
monitoring purposes and the true underlying population structures. We i) use
the results to establish the potential and limitations of fishery-dependent
data in providing a robust picture of spatiotemporal distributions; and ii)
simulate an area closure based on areas defined from the different data sources
at a range of temporal and spatial resolutions and assess their effectiveness
on reducing catches of a fish population. \\

@@

\replaced[id=PD]{Identifying}{Ensuring measures are implemented at} an
appropriate scale has been a challenge in the past that has led to ineffectual
measures with unintended consequences such as limited impact towards the
management objective or increased benthic impact on previously unexploited
areas (e.g. the cod closure in the North Sea
\citep{Rijnsdorp2001,Dinmore2003}). \replaced[id=PD]{M}{Since then m}ore
refined spatial information has \added[id=PD]{since} become available through
the combination of logbook and Vessel Monitoring System (VMS) data
\citep{Lee2010, Bastardie2010, Gerritsen2012, Mateo2016} and more real-time
spatial management has been possible \citep[e.g.][]{Holmes2011}.  Such
information is, however, derived from an inherently biased sampling programme,
targeted fishing, where fishers establish favoured fishing grounds through an
explore-exploit strategy \citep{Bailey2018} where they search for areas with
high catches and then use experience to return to areas where they've
experienced high catch in the past.  \deleted[id=PD]{ Further, fishers
	generally only recorded landings (not catch) on a daily
	basis\todo{\added[id=JJ]{Its not clear what the problem is: landings
			collected on daily basis or landings recorded rather
			than catch}}.  This leads to questions about the
	validity of inference that can be drawn from landings data assigned to
	VMS activity pings.}\todo{\added[id=JJ]{This comes as a surprise: I
		thought this was going to be about
		discards}\added[id=PD]{Agree, have removed this to avoid
		confusion}}\\

@@

To answer these questions we i) develop a simulation model where population
dynamics are highly-resolved in space and time\replaced[id=PD]{. Being}{ and
	are} known \added[id=PD]{directly} rather than inferred from sampling
or commercial catch\added[id=PD]{, we can use the population model to validate
	how inference from fisheries-dependent and fisheries independent
	sampling relates to the real population structure in a way we could not
	with real data}. We ii) compare, at different spatial and temporal
aggregations, the simulated population distributions to samples from
fisheries-dependent and fisheries independent catches to test if these are a
true reflection of the relative density of the populations. We then iii)
simulate a fishery closure to protect a species based on different spatial and
temporal data aggregations. We use these evaluations to draw inference on the
utility of commercial data in supporting management decisions.
\todo{\added[id=JJ]{If the paper has two goals this should be clear from the
		start, but may be better over 2 MSs}\added[id=PD]{I would like
		to keep both parts, but have made clearer in how its set out.
		The closure scenarios form validation of the data aggregation,
		rather than effectiveness of the closures themselves - so its a
		continuation of the same question in my eyes}}\deleted[id=PD]{.
	Further, we extend our analysis to a range of spatial and temporal
	scales to assess the impact of these processes on the success of the
	management measure.}\\

@@

The basic population level processes are simulated using a modified two-stage
Deriso-Schnute delay difference model \citep{Deriso1980, Schnute1985,
	Dichmont2003} occurring at a daily time-step. \added[id=PD]{A daily
	time-step was chosen to discretise continuous population processes on a
	biologically relevant and computationally tractable timescale.}
\replaced[id=PD]{Under the population dynamics module}{Here,} population
biomass growth and depletion for pre-recruits and\deleted[id=PD]{fish}
recruited \added[id=PD]{fish}\deleted[id=PD]{to the fishery} are modelled
separately as a function of previous recruited biomass, intrinsic population
growth and recruitment functionally linked to the adult population size.
Biomass for each cell $c$ is incremented each day $d$ as follows (the full
parameter list is detailed in Table \ref{tab: pop_variable}): \begin{equation}
	\begin{split}
	B_{c,d+1} = &\\
	& (1 + \rho) B_{c,d} \cdot e^{-Z_{c,d}} - \rho \cdot e^{-Z_{c,d}} \hspace{2.9cm}
	\times \\  
	& (B_{c,d-1} \cdot e^{-Z_{c,d-1}} + Wt_{R-1} \cdot \alpha_{d-1} \cdot
	R_{\tilde{y}(c,y,d-1)})
	\hspace{0.4cm} + \\
	& Wt_{R} \cdot \alpha_{d} \cdot R_{\tilde{y}(c,y,d)} 
	\end{split}
\end{equation}
where $\rho$ is Brody's coefficient, shown to be equal to $e^{-K}$ when $K$ is
the growth rate from a von Bertalanffy logistic growth model
\citep{Schnute1985}. $Wt_{R-1}$ is the average weight of fish prior to
recruitment, while $Wt_{R}$ is the average recruited weight. $\alpha_{d}$
represents the proportion of fish recruited during that day for the year, while
$R_{c,\tilde{y}}$ is the annual recruits in cell $c$ for year $y$. \\

@@

Recruitment is modelled through a function relating the adult biomass to
recruits at time of recruitment. In \emph{MixFishSim}, it can be modelled
either either as a stochastic Beverton-Holt stock-recruit form
\citep{Beverton1957}: 
\begin{equation}
	\begin{split}
	\bar{R}_{c,d} = & \frac{(\alpha * S_{c,d})}{(\beta + S_{c,d})} \\
	     R_{c,d} \sim & \log N[(\log(\bar{R}_{c,d}),\sigma^2)]
	\end{split}
\end{equation}
Where $\alpha$ is the maximum recruitment rate, $\beta$ the spawning stock
biomass (SSB) required to produce half the maximum stock size, $S$ current
stock size and $\sigma^2$ the variability in the recruitment due to stochastic
processes, or a stochastic Ricker form \citep{Ricker1954}:
\begin{equation}
	\begin{split}
	\bar{R}_{c,d} = & B_{c,d} * e^{(\alpha - \beta * B_{c,d})} \\	
   	     R_{c,d} \sim & \log N[(\log(\bar{R}_{c,d}),\log(\sigma^2))]
	\end{split}
\end{equation}
where $\alpha$ is the maximum productivity per spawner and $\beta$ the density
dependent reduction in productivity as the SSB increases. In our example
application the Beverton-Holt form of stock recruit relationship was used for
all populations though either functional form can be chosen.

@@

During pre-defined weeks of the year the habitat quality is modified with
\added[id=PD]{user-defined} spawning habitat locations\deleted[id=PD]{s},
\replaced[id=PD]{resulting in}{meaning} each population
\replaced[id=PD]{having}{has} concentrated areas where spawning takes place. In
the simulations the populations move\deleted[id=PD]{s} towards
\replaced[id=PD]{these cells}{this} in the weeks prior to spawning, resulting
in directional movement towards the spawning grounds.\todo{\added[id=JM]{What
		does it mean concisely? Areas are assigned?} \added[id=PD]{Yes,
		the areas are pre-defined - I have amended to reflect and tried
		to clarify}} \\

\replaced[id=JJ]{An}{, with an} advection-diffusion process\deleted[id=JJ]{to}
control\added[id=JJ]{s}\deleted[id=JJ]{how the} population\deleted[id=JJ]{s}
move\replaced[id=JJ]{ment}{d}, with a time-varying temperature covariate used
to change the interaction between time and suitable habitat on a weekly
time-step\todo{\added[id=JJ]{What have a temperature covariate? Could just use
		time}\added[id=PD]{Was intended as some biological meaning -
		species thermal tolerances load onto the temperature effect -
		so could be different per species}}.  \deleted[id=JJ]{This was
	intended to balance realism in population movement, capturing the main
	directed and random processes, and practicality of modelling the
	population rather than individual fish.} Each population $p$
\replaced[id=PD]{wa}{i}s assigned a thermal tolerance with mean,
$\mu\added[id=PD]{_{p}}$ and variance, $\sigma^2\added[id=PD]{_{p}}$ so that
each cell and population temperature suitability is defined that:
\begin{equation}
	Tol_{c, p\added[id=PD]{, wk}} = \frac{1}{ \sqrt (2\pi \cdot \sigma^2_{p})} \cdot \exp(-
		\frac{(T_{c\added[id=PD]{, wk}} - \mu_{p})^2}{2 \cdot \sigma^2_{p}} )	
\end{equation}
Where $Tol_{c, p, \added[id=PD]{wk}}$ is the tolerance of population $p$ for
cell $c$ \added[id=PD]{in week $wk$}, $T_{c, \added[id=PD]{wk}}$ is the
temperature in the cell \added[id=PD]{given the week} and
$\mu\added[id=PD]{_{p}}$ and $\sigma^2\added[id=PD]{_{p}}$ the mean and
standard deviation of the population temperature tolerance. \\

\added[id=PD]{The final process results in a population structure and movement
	pattern unique to each species, with population movement occurring on a
	weekly basis. The decision to model population movement on a weekly
	timescale was to reflect that fish tend to aggregate in species
	specific locations and range within a week is fairly limited
	[\textcolor{red}{REF!!}].  Therefore this process approximated the
	demographic shifts in fish populations throughout a year with seasonal
	spawning patterns (e.g.  Figure \ref{S-fig:5}).}

@@

The fleet dynamics can be broadly categorised into three components; fleet
targeting - which determine\replaced[id=PD]{d}{s} the fleet catch efficiency
and preference towards a particular species; trip-level decisions, which
determine\added[id=PD]{d} the initial location to be fished at the beginning of
a trip; and within-trip decisions, determining movement from one fishing spot
to another within a trip. Together, these element implement an explore-exploit
type strategy for individual vessels to maximise their catch from an unknown
resource distribution (\cite{Bailey2018}). The decision to use an individual
based model for fishing vessels was taken because fishers as a group tend to
show heterogeneity and individual rather than group dynamics
[\textcolor{red}{REF!}]. Thus this was the fleet dynamics is the productive of
individual experiences rather than pre-ordained group dynamics.

@@

Several studies \citep[e.g.][]{Hutton2004, Tidd2012, Girardin2015} have
confirmed past activity and past catch rates are strong predictors of fishing
location choice. For this reason, the fleet dynamics sub-model
include\replaced[id=PD]{d}{s} a learning component, where a vessel's initial
fishing location in a trip \replaced[id=PD]{wa}{i}s based on selecting from
previously successful fishing locations. This \replaced[id=PD]{wa}{i}s achieved
by \added[id=PD]{calculating an expected revenue based on the catches from
	locations fished} in the preceding trip as well as the same month
periods in previous years and the travel costs from the port to the fishing
grounds, and choosing randomly from the top 75 \% of fishing events
\replaced[id=PD]{as defined by the expected profit, which has a seasonal
	component}{in value}.

@@

Where several fishing vessels exploit the same fish population competition is
known to play an important role in local distribution of fishing effort
\citep{Gillis1998}. If several vessels are fishing on the same patch of fish,
local depletion and interference \added[id=JJ]{competition} will affect fishing
location choice of the fleet as a whole \citep{Rijnsdorp2000, Poos2007a}. In
order to account for this behaviour, the fishing sub-model operates spatially
on a daily time-step so that for future days the biomass available to the
fishery is reduced in the areas fished. The cumulative effect is to make
heavily fished areas less attractive as a future fishing location choice as
reduced catch rates will be experienced.

@@

We parametrised the simulation model for four populations with different
demographics; growth rates, natural mortality and recruitment functions (Table
\ref{tab:1}). Habitat preference (Figure \ref{S-fig:1}) and temperature
tolerances (Figures \ref{S-fig:3}, \ref{S-fig:4}) were unique to each
population resulting in differently weekly distribution patterns (Figures
\ref{S-fig:5}-\ref{S-fig:7}). In addition, each of the populations has two
defined spawning areas which result in the populations moving towards these
areas in pre-defined weeks (Figure \ref{S-fig:2}) with population-specific
movement rates (Table \ref{tab:1}). The individual habitat preferences and
thermal tolerances result in different spatial habitat use for each population
(Figure \ref{S-fig:9}) and consequently different seasonal exploitation
patterns (Fishing mortality in Figure \ref{S-fig:10}).

@@

The survey simulation was set up with follow a fixed gridded station design
with 100 stations fished each year, starting on day 92 \added[id=PD]{and ending
	on day 112 (5 stations per day)} with same catchability parameters for
all populations ($Q_{p} = 1$). This was so as to approximate a real world
survey design with limited seasonal and spatial coverage.

@@

The following steps are undertaken to determine closures:
\todo{\added[id=JJ]{Procedure unclear. Refer to symbols in methods section or
		switch order starting with description of data type
		etc..}\added[id=PD]{Yes, will redo}}
\begin{enumerate}
	\item Extract data source
	\item Aggregate according to desired spatial and temporal resolution
	\item Interpolate across entire area at desired resolution using simple
		kriging using the \emph{interp} function from the R package
		akima [\textcolor{red}{REF!}].
	\item Close area covering top 5 \% of catch rates 
\end{enumerate}
In total 28 closure scenarios were run which represent combinations of:

@@

The trend in fishing mortality for each species show that in most cases the
fishery closure was successful in reducing fishing mortality on the species of
interest (species 3; Figure \ref{fig:3}), though interestingly the largest
reductions in fishing mortality happened immediately after the closures,
following which the fisheries "adapted" to the closures and fishing mortality
increased again somewhat. The exception to the success was the closures
implemented based on the coarsest spatial (20 x 20) and temporal resolution
(yearly) which were ineffective with all data sources. As expected, closures
based on the "known" population distribution were most effective, with
differing degrees of success using the commercial data. Fishing mortality rates
on the other species changed in different proportions, depending on whether the
displaced fishing effort moved to areas where the populations were found in
greater or lesser density. \\

A regression tree (using the R package REEMtree [ref]) highlights that the
factor most contributing to differences in fishing mortality before and after
the closure was the population (72 \% showing that the closures were effective
for population 3), followed by data resolution (21 \%), data type (7 \%) with
the least important factor the timescale ($<$ 1 \%). In general the finer the
spatial resolution of the data used the greater reduction in fishing mortality
for population 3 after the closures (Figure \ref{fig:4}). The notable outliers
are the commercial data at the coarsest spatial resolution (20 x 20) at a
yearly and weekly timescale, where closures were nearly as effective as the
fine-scale resolution. In this case the closures were sufficiently large to
protect the population (and was as effective as when the closure was based on
the "real population"; \textcolor{red}{CHECK THIS, COULD PLOT ACTUAL CLOSURE
	LOCATIONS??}) but this may have consequences in terms of restricting a
much larger area than necessary. \\

@@

Our study evaluates the importance of data scaling and considers potential bias
introduced through data aggregation when using commercial fisheries data to
infer spatio-temporal dynamics in fisheries. Understanding how fishers exploit
multiple heterogeneously distributed fish populations with different catch
limits or conservation status requires detailed understanding of the overlap of
resources; this is difficult to achieve using conventional modelling approaches
due to species targeting in fisheries resulting in preferential sampling
\citep{Martinez-Minaya2018}. Often data is aggregated or extrapolated which
requires assumptions about the spatial and temporal scale of processes. Our
study explores the assumptions behind such aggregation and preferential
sampling to identify potential impacts on management advice. With modern
management approaches increasingly employing more nuanced spatio-temporal
approaches in order to maximise productivity while taking account of both the
biological and human processes operating on different time-frames
\citep{Dunn2016}, understanding assumptions behind the data used -
increasingly a combination of logbook and positional information from vessel
monitoring systems - is vital to ensure measures are effective. \\

We employ a simulation approach to model each of the population and fishery
processes in a hypothetical 'mixed fishery', allowing us to i) evaluate the
consequences of different aggregation assumptions on our understanding of the
spatio-temporal distribution of the underlying fish populations, and ii)
evaluate the effectiveness of a spatial closure given those assumptions. \\

Our approach captures fine scale population and fishery dynamics not usually
considered (although see \cite{Bastardie2010, Bailey2018}) which offers the
advantage that larger scale fishery patterns are emergent properties of the
system rather than the result of a statistical modelling framework. \\

WHAT'S ALREADY AVAILABLE - COMPARE AND CONTRAST
